Evaluating Cloud-Optimized HDF5 for NASA’s ICESat-2 Mission

### 2025-01-16 paper.qmd
add In HDF5 for clarity
add specific time frame.  Check if correct.

When working with large datasets, especially those that include numerous variables and nested groups, the storage of file-level metadata can become a challenge. By default, metadata associated with each dataset is stored in chunks of 4 kilobytes (KB). This chunking mechanism was originally intended to optimize storage efficiency and access speed on disks with hardware resources available more than 20 years ago. In datasets with many variables and/or complex hierarchical structures, these 4KB chunks can lead to significant fragmentation.

>>>>

When working with large datasets, especially those that include numerous variables and nested groups, the storage of file-level metadata can become a challenge. In HDF5, by default, metadata associated with each dataset is stored in chunks of 4 kilobytes (KB). This chunking mechanism was originally intended to optimize storage efficiency and access speed on disks with hardware resources available when HDF was originally designed in the 1990s. In datasets with many variables and/or complex hierarchical structures, these 4KB chunks can lead to significant fragmentation.
